Age-related changes in plant growth and traits

### 2016-05-24 scripts/Accessory_figs_20160218.Rmd
updating some endosperm + embryo weights preliminary analysis of nutrient data

#Table 2 showing seedcost breakdown into components, by species
```{r}
prop_seed_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_costs,prop_prepollen_costs,prop_dispersalcosts,prop_seed_costs)
prop_seed_costs_spp$species <- labels.spp.full()
prop_seed_costs_spp <- format(prop_seed_costs_spp, digit=2)
write.csv(prop_seed_costs_spp, file="figs2/Accessory_Costs/Table04_Prop_seed_costs_by_Species.csv",row.names=FALSE)
```
$embryo_endo_size

@@

plot(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$packaging_dispersal_per_seed,SummarySpp[["se"]]$prepollen_costs)
mod <- lm(log10(postpollen_all_per_seed)~log10(embryo_endo_size),SummarySpp[["mean"]])
words.top.left.logxy(mod)
abline(coef(mod)[1],coef(mod)[2])
abline(coef(mod)[1],1,col="red")
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
mtext(text="embryo + endosperm (mg)",side=1,line=1.5,outer=TRUE)

@@

# plot(postpollen_aborted_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
# mod <- lm(log10(postpollen_aborted_per_seed) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
# words.top.left.logxy(mod)
# y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
# slopes <- sma(postpollen_aborted_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1, log="xy",method="OLS")
# abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
# abline(slopes$groupsummary["Int"][[1]],1,col="red")
# acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

@@

#Figure 4 seed count, scaled to plant size, decreases 1:1 with seed size, while bud count decreases less steeply; indication that seed count is what is actually "programmed in"
```{r}

win.metafile("figs2/Accessory_Costs/Figure04_cost_of_flowers_vs_seed_size.wmf", height=5, width=15)
plot

>>>>

#Table 2 showing seedcost breakdown into components, by species
```{r}
prop_seed_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_costs,prop_prepollen_costs,prop_dispersalcosts,prop_seed_costs)
prop_seed_costs_spp$species <- labels.spp.full()
prop_seed_costs_spp <- format(prop_seed_costs_spp, digit=2)
write.csv(prop_seed_costs_spp, file="figs2/Accessory_Costs/Table04_Prop_seed_costs_by_Species.csv",row.names=FALSE)
```

@@

plot(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_all_per_seed,SummarySpp[["se"]]$prepollen_costs)
mod <- lm(log10(postpollen_all_per_seed)~log10(embryo_endo_size),SummarySpp[["mean"]])
words.top.left.logxy(mod)
abline(coef(mod)[1],coef(mod)[2])
abline(coef(mod)[1],1,col="red")
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
mtext(text="embryo + endosperm (mg)",side=1,line=1.5,outer=TRUE)

@@

@@

#Figure 4 seed count, scaled to plant size, decreases 1:1 with seed size, while bud count decreases less steeply; indication that seed count is what is actually "programmed in"
```{r}
win.metafile("figs2/Accessory_Costs/Figure04_cost_of_flowers_vs_seed_size.wmf", height=5, width=15)
plot
